2.2.a Preprocessing and Monthly Positivity Figures

### 2024-03-14 2_scripts/2.1.1 Canpath Data.qmd
Finished Canpath data cleaning

---
title: "2.1.1 Canpath Data Check"
format: html
editor: visual
---

@@

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

The aim of this qmd file is cleaning the Canpath data. Those code is unnecessary to publish with the project.

@@

```{r}
library(dplyr)         # Data management
library(zoo)           # year-month format
```

@@

# ser data
summary(Canpath_ser$ResearcherID)                      # N=74503, no missing
table(is.na(Canpath_ser$ResearcherID), useNA = 'ifany')
length(unique(Canpath_ser$ResearcherID))               # N=25975, duplicates due to same sample tested for multiple assays
```
#### 1.2 Merge three data
```{r}
# select the variables we need from each subset:
# qx subset:
qx_s<-select(Canpath_qx, ResearcherID, C_ADM_STUDY_DATASET, C_SDC_AGE, C_SDC_SEX,
             C_ADM_FSA)

@@

table(ser_s$rid %in% qx_mtpmiss$rid, useNA = 'ifany')
table(admin_s$rid %in% qx_mtpmiss$rid, useNA = 'ifany')

# reshape the subset
# ser_sw<-reshape(ser_s, idvar = "sid", timevar = "assay_id", direction = "wide")
# reshape is unnecessary
```
#### Data quality check of those small dataset
```{r}
# admin_s: missing
table(is.na(admin_s$rid), useNA = 'ifany')     # rid no missing, not all unique (3 duplicates)
# remove duplicates: drop the earliest sample
admin_s<-admin_s[!admin_s$sid %in% c("DB0006218", "DB0009025", "DB0009310"),]

table(is.na(admin_s$sid), useNA = 'ifany')     # sid 8349 missing
length(unique(admin_s$sid[!is.na(admin_s$sid)])) # non-missing sids all unique

@@

# need to deduplicate ser_s, only keep one of duplicated records
ser_rid_dup$id<-c(1:404)
ser_rid_dup %>%
  distinct(rid, .keep_all=TRUE) # N=163 （404-163 = 241 de-duplicated)

@@

# sid match
m2$sid_match[!is.na(m2$sid_admin) & !is.na(m2$sid_ser) &
             m2$sid_admin == m2$sid_ser]<-"match"
m2$sid_match[!is.na(m2$sid_admin) & !is.na(m2$sid_ser) &
             m2$sid_admin != m2$sid_ser]<-"mismatch"
m2$sid_match[!is.na(m2$sid_admin) & is.na(m2$sid_ser)]<-"ser miss"
m2$sid_match[is.na(m2$sid_admin) & !is.na(m2$sid_ser)]<-"admin miss"
m2$sid_match[is.na(m2$sid_admin) & is.na(m2$sid_ser)]<-"all miss"
table(m2$sid_match, useNA = 'ifany')

# work on this part later #

@@

# unique participants (rid)
summary(m2$rid)
table(is.na(m2$rid), useNA = 'ifany')          # N=21536, no missing

# unique samples (sid)
summary(m2$sid)
table(is.na(m2$sid), useNA = 'ifany')          # N=21536, no missing
length(unique(m2$sid))                         # N=21349, some pp has multiple samples
```
#### Apply FSA-province conversion
```{r}
# this chunk is provided by Y.Yu
province_fun <- function(var) {
  fsa_f = as.character(substr(var,1,1))
  prov =  ifelse(fsa_f == "A", "NL",
                 ifelse(fsa_f == "B", "NS",
                        ifelse(fsa_f == "C", "PE",
                               ifelse(fsa_f == "E", "NB",
                                      ifelse(fsa_f == "G" | fsa_f == "H" | fsa_f == "J", "QC",
                                             ifelse(fsa_f == "K" | fsa_f == "L" | fsa_f == "M" | fsa_f == "N" | fsa_f == "P", "ON",
                                                    ifelse(fsa_f == "R", "MB",
                                                           ifelse(fsa_f == "S", "SK",
                                                                  ifelse(fsa_f == "T", "AB",
                                                                         ifelse(fsa_f == "V", "BC",
                                                                                ifelse(fsa_f == "X", "NU/NT",
                                                                                       ifelse(fsa_f == "Y", "YT", NA
                                                                                       ))))))))))))

@@

## 1) group by prov (FSA converted)
  m2$region[m2$prov %in% c("NB", "NL", "NS", "PE")]<-"Atlantic"
  m2$region[m2$prov %in% c("AB")]<-"Alberta"
  m2$region[m2$prov %in% c("BC")]<-"BC"
  m2$region[m2$prov %in% c("ON")]<-"Ontario"
  m2$region[m2$prov %in% c("QC")]<- "QC"  # recode it as NA later
  m2$region[m2$prov %in% c("SK")]<- "SK & MB"
table(m2$prov, m2$region, useNA = 'ifany')

@@

## recode QC as missing
  m2$region[m2$region=="QC"]<-NA # N=4 coded as missing (NA)
```
## see what is the assay used in each region
```{r}
m2 %>%
  select(region, assay_id) %>%
  group_by(region, assay_id) %>%
  summarise(Freq=n())

# clean the data var
m2$date_col<-as.Date(m2$date_col, format = "%Y-%m-%d")
m2$date_asy<-as.Date(m2$date_asy, format = "%Y-%m-%d")

# when those assay was applied?
m2 %>%
  group_by(region) %>%
  summarise(Freq=n(),
            tcol_min = min(date_col, na.rm=T),
            tcol_max = max(date_col, na.rm=T))
```
## save the data
```{r}
Canpaths<-m2
rm(m1, m2, n_admin, ser_sw)
save(Canpaths, file = "../1_data/private/CANPATH/Canpaths.RData")
```

##===================== Part.II Estimate Seroprevalence =================

**Notes:** Seroprevalence estimation requires individual analysis and a little bit weighting. Those who has been sampled multiple times should be down-weighted properly. Those who are sampled multiple times in different months will not be down-weighted.

M.Knight's data cleaning strategy is much more straightforward, as he only need to locate the participants who provided sero data, so matching on researcherID makes senses. In our case we need to treat sero data more carefully, as in Canpath sero data, one individual could provide multiple samples, and those samples were tested by multiple assays (Abbott N/S, Mount Sinai Hosp N/S/S-RBD).

```{r}

```

##

>>>>

---
title: "2.1.1 Canpath Data Cleaning"
format: html
editor: visual
---

@@

The aim of this qmd file is cleaning the Canpath data.

In Canpath data we've removed three individuals who provided multiple samples, and several samples tested for multiple times. Those samples tested for multiple times did not result in inconsistent interpretations on assay results. See codes below for more details on data cleaning.

In cleaned ver of Canpath data all rid (researcherID, participant ID) and sid (sample ID) are unique and 1-to-1, though some sid is missing.

@@

```{r}
library(dplyr)         # Data management
# library(zoo)           # year-month format
```

@@

# ser data
summary(Canpath_ser$ResearcherID)                      # N=74503, no missing
table(is.na(Canpath_ser$ResearcherID), useNA = 'ifany')
length(unique(Canpath_ser$ResearcherID))               # N=25975, duplicates due to same sample tested for multiple assays
```

#### 1.2 Merge three data
```{r}
# select the variables we need from each subset:
# qx subset:
qx_s<-select(Canpath_qx, ResearcherID, C_ADM_STUDY_DATASET, C_SDC_AGE, C_SDC_SEX,
             C_ADM_FSA)

@@

table(ser_s$rid %in% qx_mtpmiss$rid, useNA = 'ifany')
table(admin_s$rid %in% qx_mtpmiss$rid, useNA = 'ifany')
```
#### Data quality check of those small dataset
```{r}
# admin_s: missing
table(is.na(admin_s$rid), useNA = 'ifany')     # rid no missing, not all unique (3 duplicates)
# remove duplicates: drop the earliest sample
admin_s<-admin_s[!admin_s$sid %in% c("DB0006218", "DB0009025", "DB0009310"),]

table(is.na(admin_s$sid), useNA = 'ifany')     # sid 8349 missing
length(unique(admin_s$sid[!is.na(admin_s$sid)])) # non-missing sids all unique
# remove duplicates: drop the earliest sample
ser_s<-ser_s[!ser_s$sid %in% c("DB0009310"),]

@@

# need to deduplicate ser_s, only keep one of duplicated records
ser_rid_dup$id<-c(1:402)
ser_rid_dup %>%
  distinct(rid, .keep_all=TRUE) # N=162 （402-162 = 240 de-duplicated)

@@

# sid match
m2$sid_match[!is.na(m2$sid_admin) & !is.na(m2$sid_ser) &
             m2$sid_admin == m2$sid_ser]<-"match"
m2$sid_match[!is.na(m2$sid_admin) & !is.na(m2$sid_ser) &
             m2$sid_admin != m2$sid_ser]<-"mismatch"
m2$sid_match[!is.na(m2$sid_admin) & is.na(m2$sid_ser)]<-"ser miss"
m2$sid_match[is.na(m2$sid_admin) & !is.na(m2$sid_ser)]<-"admin miss"
m2$sid_match[is.na(m2$sid_admin) & is.na(m2$sid_ser)]<-"all miss"
table(m2$sid_match, useNA = 'ifany') # no mismtach, good

# drop unnecessary sids
m2$sid<-m2$sid_ser
m2<-select(m2, -c("sid_admin", "sid_ser", "sid_match"))

@@

# unique participants (rid)
summary(m2$rid)
table(is.na(m2$rid), useNA = 'ifany')          # N=25839, no missing
length(unique(m2$rid))                         # all unique

# unique samples (sid)
summary(m2$sid)
table(is.na(m2$sid), useNA = 'ifany')          # N=21346, 4493 missing
length(unique(m2$sid[!is.na(m2$sid)]))         # N=21346, no missing all unique
```
#### Apply FSA-province conversion
```{r}
# this chunk is provided by Y.Yu
province_fun <- function(var) {
  fsa_f = as.character(substr(var,1,1))
  prov =  ifelse(fsa_f == "A", "NL",
                 ifelse(fsa_f == "B", "NS",
                        ifelse(fsa_f == "C", "PE",
                               ifelse(fsa_f == "E", "NB",
                                      ifelse(fsa_f == "G" | fsa_f == "H" | fsa_f == "J", "QC",
                                             ifelse(fsa_f == "K" | fsa_f == "L" | fsa_f == "M" | fsa_f == "N" | fsa_f == "P", "ON",
                                                    ifelse(fsa_f == "R", "MB",
                                                           ifelse(fsa_f == "S", "SK",
                                                                  ifelse(fsa_f == "T", "AB",
                                                                         ifelse(fsa_f == "V", "BC",
                                                                                ifelse(fsa_f == "X", "NU/NT",
                                                                                       ifelse(fsa_f == "Y", "YT", NA
                                                                                       ))))))))))))

@@

## 1) group by prov (FSA converted)
  m2$region[m2$prov %in% c("NB", "NL", "NS", "PE")]<-"Atlantic"
  m2$region[m2$prov %in% c("AB")]<-"Alberta"
  m2$region[m2$prov %in% c("BC")]<-"BC"
  m2$region[m2$prov %in% c("ON")]<-"Ontario"
  m2$region[m2$prov %in% c("QC")]<- "QC"  # recode it as NA later
  m2$region[m2$prov %in% c("SK", "MB")]<- "SK & MB"
table(m2$prov, m2$region, useNA = 'ifany')

@@

## recode QC as missing
  m2$region[m2$region=="QC"]<-NA # N=4 coded as missing (NA)
```

#### see what is the assay used in each region
```{r}
m2 %>%
  select(region, assay_id) %>%
  group_by(region, assay_id) %>%
  summarise(Freq=n())

# clean the date var (codes provided by M.Knight)

## The collection date var
m2$date_col1<-gsub("/","-", m2$date_col) # replace "/" with "-"
m2$date_col1<-as.Date(lubridate::parse_date_time(m2$date_col1,
                                                 c("%y-%m-%d","%m-%d-%y")),tz = "UTC")

## The assay running date var
m2$date_asy[m2$date_asy=="21-07-16"]<-"2021-07-16"
m2$date_asy1<-as.Date(m2$date_asy, format = "%Y-%m-%d")

## cleaning temp var
m2$date_asy<-m2$date_asy1
m2$date_col<-m2$date_col1
m2<-select(m2, -c("date_col1", "date_asy1"))

## Beware some discrepancies: sample collection time is later than assay date
## N=4
m2[m2$date_asy < m2$date_col &
             !is.na(m2$date_asy) & !is.na(m2$date_col),]

# when those assay was collected?
m2 %>%
  group_by(region) %>%
  summarise(Freq=n(),
            tcol_min = min(date_col, na.rm=T),
            tcol_max = max(date_col, na.rm=T))
```

#### 1.3 save the data
```{r}
Canpaths<-m2
rm(m1, m2, n_admin, ser_sw, n_ser, qx_mtpmiss, ser_rid_dup)
rm(admin_s, qx_s, qx_s_mtp, ser_s)
save(Canpaths, file = "../1_data/private/CANPATH/Canpaths.RData")

# Save to the shared folder 
save(Canpaths, file = "~/../../jmy/CANPATH/Canpaths.RData")
```

### 2024-03-14 2_scripts/2.2 Rogen-Gladen Adj.qmd
Finished Canpath data cleaning

## Load dataset
```{r}
# The CBS Ab subset data
load(file = "../1_data/private/CBS_Ab.RData")
load(file = "../1_data/private/RFD4682e.RData")
```

## Load necc paks
```{r}
library(dplyr)         # Data management
library(reshape2)      # for melt() function
library(ggplot2)        # ggplot
library(zoo)           # year-month format
```
# ============= Part I. The Changing of Anti-N Pos APL ===============#

@@

#### Apply ggplot, plot two together
```{r}
APL_melt<-melt(select(tb1, Col_Month, prop.n, prop.n_RG), id.vars = "Col_Month")

@@

# ============= Part II. The Changing of Anti-N Pos Overtime ===============#

#### Anti-N in CBS data (Roche)
```{r}
CBS_Ab %>%
  with(summary(roche_n))

@@

# Roche only
CBS_Ab %>%
  .[is.na(.$abbott_n) & !is.na(.$roche_n), ] %>%
  with(summary(sampledate))
```
## Making result table for ggplot
```{r}
# prepare melt data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

#### Apply ggplot, plot two together
```{r}
CBS_melt<-melt(select(tb1, month_year, prop.n, prop.n_RG_h, prop.n_RG_l), id.vars = "month_year")

@@

#### Plot CBS and APL all together
```{r}
# Create a merged data
APL_melt$data<-rep("APL", length(APL_melt$Col_Month))
colnames(APL_melt)<-c("month_year", "variable", "value" , "data")

@@

## What's the reason of the gap? 
```{r}
# The gap between adjusted and unadjused - Rogen-Gladen equation is the cause
# In our case, the sensitivity is where most variance come from. Specificity is good over time, and we can used the number published by the manufacturer (Roche & Abbott). Since sens is imperfect (0.8--1.0) and specificity is mostly 100% trustworthy (~1.0), the R-G equation and be simplified as:

@@

# Binary
table(CBS_Ab$interp_roche_s, useNA = 'ifany')
# Majority (87.50%) were test positive
```
#### Calculate Anti-S Positivity
```{r}
# prepare melt data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

p02$labels$colour<-"Adjustment"
p02
```
#### Add additional COI 0.8 and 15

@@

# elevating COI from 0.4 to 15 increase N(-) by 2000
```
#### Plot 03:  0.4 and 15 COI together in one single plot
```{r}
# Creating the N_prop data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

p03$labels$colour<-"COI"
p03
```
#### Add RG-adjustment to the plot, using the sens and spec related to detection of virus neutrolization, rather than detection of presence of Antibodies.
```{r}
# N and proportions
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

CBS_melt4$COI[CBS_melt4$variable %in% c("prop.s0.8", "prop.s0.8_RG")]<-"0.8"
CBS_melt4$COI[CBS_melt4$variable %in% c("prop.s15", "prop.s15_RG")]<-"15"
table(CBS_melt4$variable, CBS_melt4$COI)
```
```{r}
## ggplot using melted data
p04<-CBS_melt4 %>%
  ggplot(aes(x=month_year, y=value, colour=adj)) +
  geom_point(aes(colour=adj, shape=COI)) +
  geom_line(aes(colour=adj, linetype=COI))  +
  geom_hline(yintercept=0, colour='red', linetype=2) +
  xlab("Time") + ylab("Estimated Prevalence") +
  theme_bw()

>>>>

## Load dataset

```{r}
# The CBS Ab subset data
load(file = "../1_data/private/CBS_Ab.RData")
load(file = "../1_data/private/RFD4682e.RData")
```

## Load necc paks

```{r}
library(dplyr)         # Data management
library(reshape2)      # for melt() function
library(ggplot2)        # ggplot
library(zoo)           # year-month format
```

# ============= Part I. The Changing of Anti-N Pos APL ===============

@@

#### Apply ggplot, plot two together

```{r}
APL_melt<-melt(select(tb1, Col_Month, prop.n, prop.n_RG), id.vars = "Col_Month")

@@

# ============= Part II. The Changing of Anti-N Pos Overtime ===============

#### Anti-N in CBS data (Roche)

```{r}
CBS_Ab %>%
  with(summary(roche_n))

@@

# Roche only
CBS_Ab %>%
  .[is.na(.$abbott_n) & !is.na(.$roche_n), ] %>%
  with(summary(sampledate))
```

## Making result table for ggplot

```{r}
# prepare melt data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

#### Apply ggplot, plot two together

```{r}
CBS_melt<-melt(select(tb1, month_year, prop.n, prop.n_RG_h, prop.n_RG_l), id.vars = "month_year")

@@

#### Plot CBS and APL all together

```{r}
# Create a merged data
APL_melt$data<-rep("APL", length(APL_melt$Col_Month))
colnames(APL_melt)<-c("month_year", "variable", "value" , "data")

@@

## What's the reason of the gap?

```{r}
# The gap between adjusted and unadjused - Rogen-Gladen equation is the cause
# In our case, the sensitivity is where most variance come from. Specificity is good over time, and we can used the number published by the manufacturer (Roche & Abbott). Since sens is imperfect (0.8--1.0) and specificity is mostly 100% trustworthy (~1.0), the R-G equation and be simplified as:

@@

# Binary
table(CBS_Ab$interp_roche_s, useNA = 'ifany')
# Majority (87.50%) were test positive
```

#### Calculate Anti-S Positivity

```{r}
# prepare melt data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

p02$labels$colour<-"Adjustment"
p02
```

#### Add additional COI 0.8 and 15

@@

# elevating COI from 0.4 to 15 increase N(-) by 2000
```

#### Plot 03: 0.4 and 15 COI together in one single plot

```{r}
# Creating the N_prop data
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

p03$labels$colour<-"COI"
p03
```

#### Add RG-adjustment to the plot, using the sens and spec related to detection of virus neutrolization, rather than detection of presence of Antibodies.

```{r}
# N and proportions
tb1<-CBS_Ab%>%
  group_by(month_year) %>%
  summarise(n = n(), )

@@

CBS_melt4$COI[CBS_melt4$variable %in% c("prop.s0.8", "prop.s0.8_RG")]<-"0.8"
CBS_melt4$COI[CBS_melt4$variable %in% c("prop.s15", "prop.s15_RG")]<-"15"
table(CBS_melt4$variable, CBS_melt4$COI)
```

```{r}
## ggplot using melted data
p04<-CBS_melt4 %>%
  ggplot(aes(x=month_year, y=value, colour=adj)) +
  geom_point(aes(colour=adj, shape=COI)) +
  geom_line(aes(colour=adj, linetype=COI))  +
  geom_hline(yintercept=0, colour='red', linetype=2) +
  xlab("Time") + ylab("Estimated Prevalence") +
  theme_bw()

### 2024-03-14 2_scripts/2.2.a CBS Preprocessing and Fig.qmd
Finished Canpath data cleaning

---
title: "2.2.a CBS Preprocessing and Monthly Positivity Figures"
format: html
editor: visual
author: J.Chen (let me know if you run into any troubles with those codes)
---

@@

@@

## Load dataset
```{r}
# The CBS Data, extracted using "CITF_CBS_desc_stats.Rmd"
load(file = "../1_data/private/CBS.RData")
# Notes: Access to CBS data got denied, ask Amen for access. Y.Yuan has confirmed on 21-Feb-2024 the ver 2023-11-30 of CBS is still the most up-to-date ver.

@@

## Load necessary paks
```{r}
library(dplyr)         # Data management
library(reshape2)      # for melt() function
library(ggplot2)       # ggplot
library(zoo)           # for year-month format
```

## Load dataset
```{r}
# CBS
load(file = "../1_data/private/CBS.RData")
```

@@

#### 1.1 CBS data
```{r}
# CBS data is clean, no need for preprocessing

@@

#### 1.2 APL data
```{r}
# APL data needs additional cleaning, will update this part soon!
```

#### 1.3 Canpath data
```{r}
# Canpath data needs additional cleaning, will update this part soon!
```

@@

#### 2.1 CBS data
```{r}
# prepare melt data
tb1<-CBS%>%
  group_by(samplemonth, region, .add=TRUE) %>%
  summarise(n = n(), )

@@

## drop useless intermediate tables
rm(tb1, tb2, tb3)
```
We only applied the sens & spec from third-party studies, instead of the numbers published online by Roche.

#### 2.2 APL data
```{r}

@@

#### 2.3 Canpath data
```{r}

@@

#### Merge all three into one
```{r}

@@

#### 3.1 CBS: Make plots by region
```{r}
# Reshape meltted data
CBS_melt<-reshape2::melt(select(CBS_pr, samplemonth, region,
                                       prop.n, prop.n_RG), 
                        id.vars = c("samplemonth", "region"),
                        variable.name = "Adj",
                        value.name = "prop")

>>>>

---
title: "2.2.a Preprocessing and Monthly Positivity Figures"
format: html
editor: visual
author: J.Chen (let me know if you run into any troubles with those codes)
---

@@

For APL
For Canpath cleaning & pre-processing, please refer to "2.1.1 Canpath Data.qmd"

@@

## Load dataset

```{r}
# The CBS Data, extracted using "CITF_CBS_desc_stats.Rmd"
load(file = "../1_data/private/CBS.RData")
# Notes: Access to CBS data got denied, ask Amen for access. Y.Yuan has confirmed on 21-Feb-2024 the ver 2023-11-30 of CBS is still the most up-to-date ver.

@@

## Load necessary paks

```{r}
library(dplyr)         # Data management
library(reshape2)      # for melt() function
library(ggplot2)       # ggplot
library(zoo)           # for year-month format
```

## Load dataset

```{r}
# CBS
load(file = "../1_data/private/CBS.RData")

# Canpath - clean ver
load(file = "../1_data/private/CANPATH/Canpaths.RData")
# load from jmy foler
# load(file = "~/../../jmy/CANPATH/Canpaths.RData")
```

@@

#### 1.1 CBS data

```{r}
# CBS data is clean, no need for preprocessing

@@

#### 1.2 APL data

```{r}
# APL data needs additional cleaning, will update this part soon!
```

#### 1.3 Canpath data

**Notes:** In Canpath data we've removed three individuals who provided multiple samples, and several samples tested for multiple times. Those samples tested for multiple times did not result in inconsistent interpretation on assay results. See "2.1.1 Canpath Date.Rmd" for more details on data cleaning.

In Canpath data all rid (researcherID, participant ID) and sid (sample ID) are unique and 1-to-1, though some sid is missing.

@@

#### 2.1 CBS data

```{r}
# prepare melt data
tb1<-CBS%>%
  group_by(samplemonth, region, .add=TRUE) %>%
  summarise(n = n(), )

@@

## drop useless intermediate tables
rm(tb1, tb2, tb3)
```

We only applied the sens & spec from third-party studies, instead of the numbers published online by Roche.

#### 2.2 APL data

**Notes:** Seroprevalence estimation requires individual analysis and a little bit weighting. Those who has been sampled multiple times should be down-weighted properly. Those who are sampled multiple times in different months will not be down-weighted.

```{r}

@@

#### 2.3 Canpath data

```{r}

@@

#### Merge all three into one

```{r}

@@

#### 3.1 CBS: Make plots by region

```{r}
# Reshape meltted data
CBS_melt<-reshape2::melt(select(CBS_pr, samplemonth, region,
                                       prop.n, prop.n_RG), 
                        id.vars = c("samplemonth", "region"),
                        variable.name = "Adj",
                        value.name = "prop")
